### 2014-03-07 docs/related-work.tex
Some related work and outline.

\documentclass{article}

@@

@@

\cite{foci12-winter}

>>>>

\documentclass{article}
\usepackage{url}

@@

% VPN arms race
% We seek to build a system that remains difficult to block even after it has many users.

@@

Broadly speaking, there are two main challenges to proxy-based circumvention.
The first is obfuscation: making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
The second is proxy address unblockability: making it difficult for
the censor simply to block proxies by address.
Past works have considered one or both of these problems.

There are different approaches to obfuscation.
One technique is to look unlike anything forbidden by the censor; that is, fail to match a blacklist.
Another is to resemble a protocol that is explicitly allowed; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports
whose payloads are indistinguishable from a uniformly random byte stream.
A examples of such a transport is obfsproxy~\cite{obfsproxy},
long the go-to obfuscated transport used by Tor.
ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its payloads,
but takes additional steps to obscure its signature of packet lengths and timing,
and is designed to resist active scanning for proxies
(the proxy server says nothing until the client proves knowledge of a shared secret).

Another path to obfsucation is the steganographic approach:
look like something the censor doesn't block.
stegotorus
freewave
codetalker tunnel (skypemorph)
fte
dust

Difficulties of look-like-something transports:
the parrot is dead
cover your acks

Tor has long faced the problem of its entry relays being blocked.
The list of relays is public, so it easy to block all of them by IP address.
Tor bridges~\cite{tor-blocking} are relays that are not universally known,
intended to serve as entry points for censored users.
A system called BridgeDB seeks to provide a few bridges to anyone who asks,
while at the same time making it difficult to learn the entire list of secret bridges.
The plain Tor protocol remains relatively easy to detect,
so BridgeDB is also capable of distributing obfsproxy and ScrambleSuit bridges.

telex
censorspoofer
no direction home

Flash proxy~\cite{flashproxy-pets12} attempts to address the problem of proxy diversity
by conscripting web users as temporary proxies.
Proxies last only as long as a web user stays on a page, so the pool of proxies is
constantly changing and difficult to block.
Their approach to proxy unblockability is in a sense opposite to this work's:
where flash proxy uses many, cheap, unreliable proxies,
we use just one high-value proxy, to block which would cause expensive collateral damage.
There exists a prototype transport that combines flash proxy with obfsproxy~\cite{obfs-flash},
however it is limited because it is not possible to obfuscate flash proxy's outermost WebSocket layer.

A technique known as OSS~\cite{oss}, for ``online scanning systems,''
closely resembles ours in important ways.
It uses a third-party web service as a conduit to carry traffic,
encoded either in a URL or in an HTTP body.
Because web services cannot in general be assumed to reproduce a web server's
response exactly
(a translation service, for example, returns a response after translating it to another language),
OSS does not use response bodies to carry data,
instead requiring the relay to initiate a reflected request back to the client.
OSS also does not claim that any one service is difficult to block, rather that there are many web services that can be used.
The main ways in which this work differs is that we effectively control the OSS:
we can count on response bodies being preserved and so use them to send downstream data;
and we put the OSS on infrastructure that is expensive to block.

How the GFW is blocking Tor.
\cite{foci12-winter}

GoAgent

% CORDON? Say how meek would be classified in it?
